
\documentclass[../include.tex]{subfiles}
\begin{document}
	\renewcommand{\bibname}{REFERENCES}
	\bibliographystyle{ieeetr}
\begin{thebibliography}{99}
	\thispagestyle{headings}
	\addcontentsline{toc}{chapter}{\numberline{}References}

	\bibitem{awrascle} {\sc A. Aw, and M. Rascle},
	{\em Resurrection of "second order" models of traffic flow}, SIAM J. Appl. Math., 60 (2000), pp. 916-938.

	\bibitem{bateman} {\sc H. Bateman},
	{\em Some recent researches on the motion of fluids}, Monthly Weather Rev. 43 (1915), 63-170.

	\bibitem{batchelor} {\sc G. K. Batchelor}
	{\em An introduction to fluid dynamics}, Cambridge University Press, Cambridge, 1967.

	\bibitem{borisbook} {\sc J. P. Boris, and D. L. Book},
	{\em Flux corrected transport I, SHASTA, a fluid transport algorithm that works}, J. Comput. Phys., 11 (1973), pp. 38-69.

	\bibitem{burgers} {\sc J. M. Burgers},
	{\em A mathematical model illustrating the theory of turbulence}, Adv. Appl. Mech. 1 (1948), 171-199.

	\bibitem{cengel} {\sc Y.A. Cengel, and J. M. Cimbala}
	{\em Fluid mechanics: Fundamentals and Applications.} Boston: McGraw-Hill, 2006.

	\bibitem{cole} {\sc J. D. Cole},
	{\em On a quasilinear equation occurring in aerodynamics}, Q. Appl. Math. 9 (1951), 225-236.

	\bibitem{daganzo} {\sc C. F. Daganzo},
	{\em Requiem for second-order fluid approximations of traffic flow}, Transport. Res. B, 29B (1995), pp. 277-286.

	\bibitem{kundu} {\sc P. K. Kundu, I. M. Cohen, and D. R. Dowling},
	{\em Fluid Mechanics, 5th ed.}. San Diego, Academic Press, 2011

	\bibitem{feist} {\sc M. Feistauer},
	{\em Mathematical methods in fluid dynamics}. Longman, 1993.

	\bibitem{forsyth} {\sc A. R. Forsyth},
	{\em The Theory of Differential Equations}, Cambridge University Press, Cambridge, 1890, 1900, 1902, 1906.

	\bibitem{frolk} {\sc P. Frolkovič},
	{\em Prúdenie kvapalín a plynov}. STU Bratislava, 2013.

	\bibitem{gadelhak} {\sc M. Gad-el-Hak}, "Fluid mechanics from the Beginning to the Third Millenium,"
	{\em Intl. J. of Engineering Education, } vol. 14, no.3, 1998, pp. 177-185.

	\bibitem{greenshields} {\sc B. N. Greenshields},
	{\em A study of traffic capacity}, In Proceedings of the 14th Annual Meeting of the Highway Research Board, 1934, pp. 448-474.

	\bibitem{hopf} {\sc E. Hopf},
	{\em The partial differential equation $ u_t + u\,u_x = \mu\, u_{xx} $}, Commun. Pure Appl. Math. 3 (1950), 201-230.

	\bibitem{algoritmy} {\sc G. Ibolya, and K. Mikula},
	{\em Numerical solution of the 1D viscous Burgers' and traffic flow equations by the inflow-implicit/outflow-explicit finite volume method}, ALGORITMY 2020 - 21st Conference on Scientific Computing, Vysoké Tatry - Podbanské, Slovakia, September 10 - 15, 2020. Proceedings of contributed papers, Editors: P.Frolkovič, K.Mikula and D. Ševčovič, Vydavateľstvo SPEKTRUM STU, 2020, ISBN: 978-80-227-5032-5, pp. 191-200.

	\bibitem{kachroo-sastry} {\sc P. Kachroo, and S. Sastry},
	{\em Traffic flow theory: Mathematical Framework.} University of California Berkeley, 2012.

	\bibitem{lev} {\sc R.J. LeVeque},
	{\em Finite Volume Methods for Hyperbolic Problems}, Cambridge Texts in Applied Mathematics. Cambridge University Press, 2002.

	\bibitem{lev_fdm} {\sc R.J. LeVeque},
	{\em Finite Difference Methods for Ordinary and Partial Differential Equations}, SIAM, 3600 University City Science Center Philadelphia, 2007.

	\bibitem{lighthillwitham} {\sc M. J. Lighthill, and G. B. Whitham},
	{\em On kinematic waves II: A theory of traffic flow on long crowded roads}, Proc. Roy. Soc. London Ser. A, (1955), pp. 317-345.

	\bibitem{iioe0} {\sc K. Mikula, and M. Ohlberger},
	{\em A new Inflow-Implicit/Outflow-Explicit Finite Volume Method for Solving Variable Velocity Advection Equations}, Preprint 01/10 - N, Angewandte Mathematik und Informatik, Universitaet M\"{u}nster, June 2010

	\bibitem{iioe1} {\sc K. Mikula, and M. Ohlberger},
	{\em Inflow-Implicit/Outflow-Explicit Scheme for Solving Advection Equations}, in Finite Volumes in Complex Applications VI, Problems \& Perspectives, Eds.J.Fo\u{r}t et al. (Proceedings of the Sixth International Conference on Finite Volumes in Complex Applications, Prague, June 6-10, 2011), Springer Verlag, 2011, pp. 683-692.

	\bibitem{iioe2012} {\sc K. Mikula, M. Ohlberger, and J. Urban},
	{\em Inflow-Implicit/Outflow-Explicit Finite Volume Methods for Solving Advection Equations}, Technical Report 01/12 - N, FB 10, Universitaet Muenster, Number 01/12 - N - February 2012.

	\bibitem{iioe2} {\sc K. Mikula, M. Ohlberger, and J. Urban},
	{\em Inflow-Implicit/Outflow-Explicit finite volume methods for solving advection equations}, Applied Numerical Mathematics, Vol. 85 (2014) pp. 16-37

	\bibitem{olv} {\sc P. J. Olver},
	{\em Introduction to Partial Differential Equations}, Undergraduate Texts in Mathematics. Springer, New York, 2014.

	\bibitem{patankar} {\sc S. V. Patankar},
	{\em Numerical Heat Transfer and Fluid Flow}. Hemisphere Publishing Corporation, New York, 1980.

	\bibitem{reddy} {\sc J. N. Reddy}
	{\em An Introduction to the Finite Element Method}. McGraw-Hill Education, New York, 2005.

	\bibitem{richards} {\sc P. I. Richards},
	{\em Shock waves on highways}, Oper. Res., 4 (1956), pp. 42-51.

	\bibitem{mathshistory}  {\sc E. Robertson, J. O'Connor}
	{\em MacTutor History of Mathematics Archive}, School of Mathematics and Statistics, University of St Andrews. https://mathshistory.st-andrews.ac.uk/Biographies/

	\bibitem{trafficmono} Transportation Research Board ACP50, Committee on Traffic Flow Theory and Characteristics, Traffic Flow Theory Monographs,
	http://tft.eng.usf.edu/docs.htm

	\bibitem{wageningen} {\sc F. van Wageningen-Kessels, H. van Lint, K. Vuik, and \\S. Hoogendoorn}
	{\em Genealogy of traffic flow models}, EURO Journal on Transportation and Logistics, 4(4):445-473, 12 2015.

	\bibitem{white} {\sc F. M. White},
	{\em Fluid mechanics, 7th ed.}, New York: McGraw-Hill, 2009.

	\bibitem{whitham} {\sc G. B. Whitham},
	{\em Linear and Nonlinear Waves}, Wiley-Interscience, 1974.

	\bibitem{zalesak} {\sc S. T. Zalesak},
	{\em Fully multidimensional flux corrected transport algorithms for fluids}, J. Comput. Phys., 31 (1979), pp. 335-362.

	\bibitem{zhang} {\sc H. M. Zhang},
	{\em A theory of nonequilibrium traffic flow}. Transportation Research B, 32:485-498, 1998.
\end{thebibliography}
\end{document}